\section{Energy and Power}
\subsection{Power vs Energy}
Power and energy are related but distinct concepts in physics. 
Power is the rate at which energy is transferred or converted, while energy is the capacity to do work.
Reducing power consumption doesn't necessarily reduce energy consumption, as it depends on the duration of the operation. 
The optimization of power isn't the same as the optimization of energy, and both are important considerations in the design of efficient systems.
To minimize power consumption we use thermal constraints, while to minimize energy consumption we use battery constraints.
In autonomous systems, energy consumption goes through a well-defined path:
\begin{itemize}
    \item \textbf{Energy generation}
    \item \textbf{Energy storage}
    \item \textbf{Energy conversion}
    \item \textbf{Energy consumption}
\end{itemize}
So we understand that a System Designer is necessary to optimize the energy path.
\subsection{Power Source}
Energy harvesting is the process of capturing and converting ambient energy from the environment into usable electrical energy.
There is a wide range of physical phenomena that can be harnessed for energy harvesting, including:
\begin{itemize}
    \item \textbf{Piezoelectricity}
    \item \textbf{Thermoelectricity}
    \item \textbf{Electromagnetic induction}
    \item \textbf{Photovoltaic effect}
    \item \textbf{Triboelectricity}
\end{itemize}
There same issues that affect the design of energy harvesting systems include:
\begin{itemize}
    \item \textbf{The maximum power extraction}: The maximum power that can be extracted from an energy harvesting source is often limited by the environmental conditions.
    \item \textbf{Extracted power is almost invariably very low}: The power generated by energy harvesting sources is typically very low, which can limit their applicability in certain applications.
    \item \textbf{Extracted power might not be needed immediatly}: To avoid this problem is needed to store the energy in a battery or supercapacitor, which can add complexity and cost to the system.
\end{itemize}
